Analysis paper

### 2021-04-08 analysis/analysis.Rmd
first proposal to divide epidemic

>>>>

## Visualisation of data

truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
  , .(location_name, target_end_date, target_type, true_value)] %>%
  unique()

truth <- truth[order(location_name, target_type, target_end_date)]

epi_classification <- function(actual_value, first_diff, threshold = 0.05) {
  out <- ifelse(first_diff > 0, "rising", "falling")
  out[abs(first_diff) < 0.05 * actual_value] <- "stable"
  return(out)
}

truth[, first_diff := c(NA, diff(true_value)), 
      by = c("location_name", "target_type")]
truth[, epi_class := epi_classification(true_value, first_diff), 
      by = c("location_name", "target_type")]
truth[, shift_date := shift(target_end_date, -1), 
      by = c("location_name", "target_type")]
# truth[, second_diff := c(NA, diff(first_diff)), 
#       by = c("location_name", "target_type")]

ggplot(truth, aes(x = target_end_date)) + 
  geom_rect(aes(xmin = target_end_date, xmax = shift_date, ymin = -Inf, ymax = Inf, fill = factor(epi_class)), alpha = 0.2) +
  geom_line(aes(y = true_value, color = "truth")) + 
  geom_line(aes(y = first_diff, color = "first diff")) +
  labs(y = "value", x = "date") + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")
